


Homework 0 - Team 4 Duke Dinosaurs
========================================================

### Implementation

<!--
Use this section to implement the fizzbuzz function.

This should include a short write up describing your appraoch
to implementing the function. Not both code formating / style
and your writeup matter for your overall grade.
-->

The layout of our function is simple. Inside a function that we are
storing inside variable "FizzBuzz", we used If Statements and For Loops
to solve the problem.
 
Our function's input value is "n". 

Inside our function, the first If Statement tells the function that 
should the input n not be a vector (using "!" to symbolize not), the 
function should stop running the function and give an error message 
"Please input ...".
 
The next If Statement says that should our input modulo 1 not equal 0,
the function will stop running and the same error message will appear.
Since non-integers, such as 2.5, modulo 1 will not produce a 0; 
2.5%%1=0.5. 

The next If Statement says that should the length of our input n equal 1, 
n should be a vector composed of the sequence from 1 to n. 

In our For Loop, we specify some conditions for the elements, x, inside n. 

Our If Statement says that if the element modulo 15 equals 0, the word
"FizzBuzz" will print. 

For the cases where the element modulo 15 doesn't equal 1, if the element 
modulo 3 equals 0, the word "Fizz" will print.

For the cases where the first two conditions aren't met, if the element 
modulo 5 equals 0, the word "Buzz" will print. 

For all the remaining cases, the element will just print itself. 

We then call our function with the command FizzBuzz and let our input n
equal 100. 

In conclusion, we first specified the conditions for the function's 
input. We then looped into the sequence we created to determine what 
should appear within that sequence and when it should appear. Lastly, 
we ran the function.
 
```{r} 
FizzBuzz = function(n) {
 if(!is.vector(n)){
    stop("Please input a integer or a vector of integers.")
  }
  if(!all(n%%1==0)){
    stop("Please input a integer or a vector of integers.")
  }
  if(length(n)==1){
    n <- 1:n
  }


for (x in n){
    if (x%%15==0) print("FizzBuzz")
    else if (x%%3==0) print("Fizz") 
    else if (x%%5==0) print("Buzz")
    else 
    print(x)
  }
}

FizzBuzz(n=100)

```

### Output

<!--
Use this section to show the output of your 
fizzbuzz function for integer values from 1 to 100.

No writeup is necessary for this section.
-->

```{r}

```
